\documentclass[10pt,a4paper]{article}

\usepackage[left=2cm,right=2cm,top=1.2cm,bottom=1.2cm]{geometry}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{tikz}
\usepackage{enumitem}

% -----------------------------------------------------------------------------
% TYPOGRAPHY & COLORS (Matching ResumeKt)
% -----------------------------------------------------------------------------
% Fonts
\usepackage[rm]{roboto}
\usepackage[defaultsans]{lato}
\renewcommand{\familydefault}{\sfdefault}

% Colors
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelRed}{HTML}{450808}
\definecolor{PastelRed}{HTML}{8F0D0D}
\definecolor{GoldenEarth}{HTML}{E7D192}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=PastelRed,
    urlcolor=PastelRed,
    pdfborder={0 0 0}
}

\begin{document}
\pagestyle{empty} % No page numbers for single page look

% -----------------------------------------------------------------------------
% HEADER (Enhanced Premium Design)
% -----------------------------------------------------------------------------
\begin{center}
    {\Huge\bfseries\rmfamily\color{DarkPastelRed} Kiran Tilekar}\\[0.3cm]
    {\Large\bfseries\color{PastelRed} Senior Java Developer | Spring Boot Expert}\\[0.4cm]
    
    % Contact info with enhanced design
    \colorbox{black!3}{%
        \begin{minipage}{0.95\textwidth}
            \centering
            \vspace{0.25cm}
            {\small\color{SlateGrey}
            % Primary contact methods with subtle emphasis
            \colorbox{PastelRed!10}{\color{DarkPastelRed}\faEnvelope\ \href{mailto:kirantilekar@icloud.com}{\textbf{kirantilekar@icloud.com}}} 
            \enspace\textbullet\enspace
            \colorbox{PastelRed!10}{\color{DarkPastelRed}\faPhone\ \textbf{+91-9834882015}}
            \enspace\textbullet\enspace
            \faMapMarker*\ Pune, India\\[0.2cm]
            % Social links
            \faLinkedin\ \href{https://linkedin.com/in/kiran-tilekar-94173382}{\textbf{kiran-tilekar}} 
            \enspace\textbullet\enspace
            \faGithub\ \href{https://github.com/Kt129673}{\textbf{Kt129673}}
            }
            \vspace{0.25cm}
        \end{minipage}
    }
\end{center}

\vspace{0.1cm}
\noindent\textcolor{GoldenEarth}{\rule{\textwidth}{1.5pt}}
\vspace{0.3cm}

% -----------------------------------------------------------------------------
% COVER LETTER BODY
% -----------------------------------------------------------------------------

\today

\vspace{0.3cm}

% Recipient Details with enhanced styling
\noindent
\begin{minipage}{0.6\textwidth}
    {\color{DarkPastelRed}\textbf{Hiring Manager}}\\
    {\color{SlateGrey}\textbf{\textit{Company Name}}}\\
    {\color{LightGrey}\textit{Company Address}}\\
    {\color{LightGrey}\textit{City, State, ZIP Code}}
\end{minipage}

\vspace{0.3cm}

\noindent{\color{DarkPastelRed}\textbf{Subject:}} {\color{SlateGrey}Application for Senior Java Developer -- Enterprise Systems \& High-Availability Architecture}

\vspace{0.3cm}

\noindent Dear Hiring Manager,

\vspace{0.2cm}

With over \textbf{3.3 years of experience} delivering mission-critical enterprise systems at \textbf{AVICS}, I specialize in building robust \textbf{Spring Boot applications} that perform flawlessly under pressure. I architect government financial platforms servicing multiple Zilla Parishads with \textbf{99.9\% uptime} and \textbf{sub-200ms latency} for \textbf{50,000+ monthly transactions}. My approach combines technical excellence with a relentless focus on reliability, security, and performance optimization.

At \textbf{AVICS}, I've been instrumental in architecting and delivering enterprise-grade government systems that demand absolute precision and zero tolerance for failure. My development philosophy centers on three core principles: \textbf{build for reliability from day one}, \textbf{optimize proactively}, and \textbf{treat security as non-negotiable}. This mindset has enabled me to consistently deliver systems that exceed performance benchmarks while maintaining impeccable data integrity. 

Key achievements at \textbf{AVICS} include:
\begin{itemize}[leftmargin=*,label={\color{PastelRed}\faCheckCircle}]
    \item \textbf{Engineering Zero Data Loss:} Designed double-entry bookkeeping systems for government treasuries that have maintained \textbf{100\% data integrity} across millions of multi-year financial transactions.
    \item \textbf{High-Performance Architecture:} Proactively optimized database queries and implemented multi-level caching strategies (Redis/Caffeine) to achieve \textbf{sub-200ms latency} and \textbf{40\% reduction} in database load for 50,000+ monthly transactions.
    \item \textbf{Automated Reporting Excellence:} Built automated statutory reporting pipelines using JasperReports that generate \textbf{20+ critical government reports}, saving \textbf{30+ hours/week} while ensuring 100\% accuracy.
    \item \textbf{Security-First Development:} Implemented enterprise-grade security with Spring Security, JWT/OAuth2, and RBAC, protecting financial transactions worth over \textbf{Rs.500+ Cr} with zero security incidents.
\end{itemize}

Beyond core development, I bring modern expertise in \textbf{Cloud-Native architectures} (AWS/Azure) and \textbf{IoT systems}. I recently architected a data harvesting platform ingesting 10,000+ points/minute, designing self-healing mechanisms that ensure continuity even during network failures.

I am eager to bring this expertise in \textit{backend architecture}, \textit{performance optimization}, and \textit{cloud-native development} to \textbf{\textit{Company Name}}. I am confident that my ability to write clean, scalable, and highly resilient code aligns with your engineering standards.

I look forward to discussing how I can contribute to your team's success. Thank you for your time and consideration.

\vspace{0.6cm}

\noindent Sincerely,

\vspace{0.6cm}

\noindent\textbf{Kiran Tilekar}\\
{\small Senior Java Developer}

\end{document}
